---
title: "Create a web page using R Markdown and Leaflet."
author: "Olivier Detandt"
date: "25 October 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##Introduction

This is an Coursera project defined as follow=
"Create a web page using R Markdown that features a map created with Leaflet.

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!"



## Data plotted

The data used come from http://www.worldatlas.com/articles/most-dangerous-cities-in-the-united-states.html

This show the most Dangerous Cities In The United States



```{r,wrnings=FALSE, message=FALSE }
setwd("C:/Users/olivier.detandt/Documents/Doc/DataScience/Product Development")
data<-read.csv("Map.csv",sep=";")

library(leaflet)
my_map <- data %>%
        leaflet() %>%
        addTiles() %>%
        setView(lng = -85, lat = 40, zoom = 5) %>%

        addMarkers(popup = "Test", 
                   lng = data$Lat, 
                   lat = data$Long)%>% 
        addCircles(weight=1,radius=sqrt(data$HomicieRate)*30000)

my_map
```


